---
title: "hotel_bookings_main"
author: "Jonathan"
date: "9/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

**The main R file for analyzing hotel_bookings dataset**
In this project we will be investigating about questions regarding about:
1. The cheapest time to book a hotel  
2. Optimal length of stay at a hotel   
3. Do the prices of hotel differ between different countries  
3.5. If so, which country offers the most expensive hotels  

TBC.

```{r read dataset and import libraries}
library(tidyverse)
library(ggplot2)

hotel_bookings <- read.csv("~/Documents/GitHub/jonathankang830/R_Projects_self/hotel_bookings/hotel_bookings.csv")
str(hotel_bookings)
```

## Data Cleaning

Clean the data by
  a) lubricate dates from chr to date format,  
  b) replace null to 0,  
  c) remove columns that may be unnecessary for our questions
  

```{r clean}
hotel_bookings_1 <- hotel_bookings %>% select(-agent, -company) %>%
  lubridate::ymd(reservation_status_date)
head(hotel_bookings_1)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
